High-Performance Primitives for Distributed Memory Architectures using Asynchronous Events

### 2012-11-12 doc/llr-pldi2013/conclusion.tex
conc

As large supercomputers continue to scale, the latencies associated
with common operations such as communication and synchronization will
become larger and more variable.  To effectively hide these latencies
future programming systems will need to compose asynchronous operations
to overlap long latency operations with useful work.  We have
presented a low-level programming interface that is fully asynchronous
including a new synchronization primitive called a deferred lock.
Our interface uses events to compose asynchronous operations.  Clients
can use events to explicitly specify dependences between operations,
giving the runtime the flexibility to schedule them in a way that maximizes latency 
hiding while still obeying dependences.

We've presented an implementation of our interface that is capable of running
on a large heterogeneous cluster containing both CPUs and GPUs.  We
employed micro-benchmarks to show that our implementation is efficient.
We also demonstrated that our interface is capable of supporting Legion,
an advanced high-level runtime system that fully leverages the asynchronous
features of our interface.  We showed that for three real-world applications
the asynchronous Legion implementations were between 22\% to 135\% faster than
implementations which contained blocking operations.

>>>>

As supercomputers continue to grow, the latencies of communication and
synchronization will become larger and more variable.  Effectively
hiding latency in future programming systems will require composing
asynchronous operations to overlap long latency operations with useful
work.  We have presented a low-level programming interface that is
fully asynchronous, including deferred locks, a new synchronization
primitive.  Asynchronous operations are composed using events, which
specify dependences between operations, giving the
runtime the flexibility to schedule operations to maximize latency
hiding while still obeying dependences.

%We've presented an implementation of our interface that is capable of running
%on a large heterogeneous cluster containing both CPUs and GPUs.  We
%employed micro-benchmarks to show that our implementation is efficient.
%We also demonstrated that our interface is capable of supporting Legion,
%an advanced high-level runtime system that fully leverages the asynchronous
%features of our interface.  We showed that for three real-world applications
%the asynchronous Legion implementations were between 22\% to 135\% faster than
%implementations which contained blocking operations.
